Comparing human and model-based forecasts of COVID-19 in Germany and Poland

### 2021-10-13 analysis/analysis.Rmd
update SI

# create helper function to make table
# ------------------------------------------------------------------------------
score_table <- function(scores, 
                             group = TRUE, 
                             full_width = TRUE) {
  # copy data, change names, round column values and reduce to sign. digits
  scores <- as.data.table(scores)
  setnames(scores, 
           old = c("horizon", "model", "target_type", "interval_score", "aem", 
                   "relative_skill", "scaled_rel_skill", "sharpness", 
                   "underprediction", "overprediction", "bias", 
                   "50", "90", "location_target", "target_phase"), 
           new = c("Horizon", "Model", "Target", "WIS", "Abs. error", 
                   "rel. skill", "WIS - rel.", "Sharpness", 
                   "Underpred.", "Overpred.", "Bias", 
                   "50%-Cov.", "90%-Cov.", "Target", "Target"), 
           skip_absent = TRUE)

@@

  table <- scores[,!c("Target")] %>%
    kable(format = "html", col.names = c(" ", names(scores)[-(1:2)])) %>% #format = "markdown"
    collapse_rows(columns = 1) %>%
    kable_styling(bootstrap_options = "striped", 
                  full_width = full_width) %>%
    column_spec(1, background = "white")

  if (group) {
    table <- table %>%
      pack_rows("Cases", 1, case_rows, indent = FALSE) %>% 
      pack_rows("Deaths", case_rows + 1, nrow(scores), indent = FALSE)
  }

@@

  # no idea how to do that in data.table: 
  df <- df %>%
    dplyr::group_by(horizon, target_type) %>%
    dplyr::mutate_at(percentage_cols, 
                     ~ paste0(., " (", 
                              round(100 * ./.[model %in% c("Hub-ensemble", 
                                                           "Hub-ensemble-mean")]), 
                              "%)"))

@@

  # tables for 1-2 weeks ahead and 3-4 weeks ahdead
  table <- score_table(df[horizon <= 2]) 
  save_kable(table, file = here(output_dir, 
                                paste0(plotname, "_", 2, "_ahead.png")))

  table <- score_table(df[horizon > 2]) 
  save_kable(table, file = here(output_dir, 
                                paste0(plotname, "_", 4, "_ahead.png")))
}

@@

filtered_data[model %in% regular_models] %>%
  filter(!(forecast_date %in% as.character(forecast_dates$death_not_scored))) %>%
  make_table(plotname = "table_mean-late-period")

@@

*Figure 2. Top: Distribution of the scaled relative skill scores for the different model and forecast targets. The vertical black line represents the baseline model. Models beat the baseline more easily for death forecasts. The renewal model had by far the most variance in terms of its performance, while the crowd forecasting model seems most consistent. Bottom: Distribution of scaled relative skill in different phases of the epidemic. The epidemic was classified as 'increasing', if the forecast point and the two data points before form a monotonically rising line, 'decreasing' if numbers were falling and 'unclear' otherwise. This plot seems like a lot of noise to me, but unsure.*

@@

<!-- **Further things we could look at** -->

<!-- - maybe look at correlation between the number of weekly cases and the score? -->

<!-- - maybe it would be interesting to look at other baseline models, e.g. "how hard is it to beat a model that just always continues the trend?" -->

<!-- - look at crowd performance as a function of the number of forecasts -->

maybe leave that to a second paper --\>

@@

dt %>%
  ggplot(aes(y = `number of forecasters`, x = forecast_date)) + 
  geom_line() + 
  facet_wrap(location_name ~ target_type)

>>>>

# create helper function to make table
# ------------------------------------------------------------------------------
score_table <- function(scores, 
                        group = TRUE, 
                        full_width = TRUE) {
  # copy data, change names, round column values and reduce to sign. digits
  scores <- as.data.table(scores)
  setnames(scores, 
           old = c("horizon", "model", "target_type", "interval_score", "aem", 
                   "relative_skill", "scaled_rel_skill", "sharpness", 
                   "underprediction", "overprediction", "bias", 
                   "50", "90", "location_target", "target_phase"), 
           new = c("Horizon", "Model", "Target", "WIS", "Abs. error", 
                   "rel. skill", "WIS - rel.", "Dispersion", 
                   "Underpred.", "Overpred.", "Bias", 
                   "50%-Cov.", "90%-Cov.", "Target", "Target"), 
           skip_absent = TRUE)

@@

  table <- scores[,!c("Target")] %>%
    kable(format = "latex", booktabs = TRUE, 
          align = c("l", "l", rep("c", 9)),
          col.names = c(" ", names(scores)[-(1:2)])) %>%
    collapse_rows(columns = 1) %>%
    kable_styling(latex_options = c("scale_down", 
                                    "hold_position")) %>%
    column_spec(1, background = "white")

  if (group) {
    table <- table %>%
      pack_rows("Cases", 1, case_rows, indent = FALSE, 
                hline_after = TRUE) %>% 
      pack_rows("Deaths", case_rows + 1, nrow(scores), indent = FALSE, 
                hline_after = TRUE)
  }

@@

  # no idea how to do that in data.table: 
  df <- df %>%
    dplyr::group_by(horizon, target_type) %>%
    dplyr::mutate_at(percentage_cols, 
                     ~ paste0(., " (", 
                              round(./.[model %in% c("Hub-ensemble", 
                                                     "Hub-ensemble-mean")], 2), 
                              ")"))

@@

  # tables for 1-2 weeks ahead and 3-4 weeks ahdead
  table <- score_table(df[horizon <= 2])

  saveRDS(object = table, 
          file = here("analysis", "plots", paste0(plotname, "_", 2, "_ahead.rds")))

  table <- score_table(df[horizon > 2]) 
  saveRDS(object = table, 
          file = here("analysis", "plots", paste0(plotname, "_", 4, "_ahead.rds")))
}

@@

filtered_data[model %in% regular_models] %>%
  filter(!(forecast_date %in% as.character(forecast_dates$death_not_scored))) %>%
  make_table(plotname = "table-late-period")

@@

@@

@@

dt[, location_target := paste0(str_to_title(target_type), 
                               "s", " in ", location_name)]

dt %>%
  ggplot(aes(y = `number of forecasters`, x = forecast_date)) + 
  geom_line() + 
  facet_wrap(~ location_target) + 
  theme_minimal() + 
  labs(y = "Number of forecasters", x = "Date")

ggsave(filename = here("analysis", "plots", "number-forecasters.png"))
```

### 2021-10-13 manuscript/manuscript.Rmd
update SI

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, 
                      out.width = "100%", 
                      fig.pos = "H", out.extra = "")
```

@@

```{r}
caption <- "Visualisation of aggregate performance metrics across forecast horizons. A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons. WIS is decomposed into its components sharpness, over-prediction and under-prediction. C: Empirical coverage of the 50\\% prediction intervals (50\\% coverage is perfect). D: Empirical coverage of the 90\\% prediction intervals. E: Sharpness (same as in panel A, B). Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score. F: Bias, i.e. general (relative) tendency to over- or underpredict. Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally. G: Absolute error of the median forecast (lower is better). H. Standard deviation of all WIS values for different horizons"
```

```{r agg-performance-all, fig.cap=caption}
knitr::include_graphics("../analysis/plots/aggregate-performance-all-v4.png")
## change name to v4
```

```{r}
caption <- "A, C: Visualisation of two week ahead forecasts against the true observed values. The shape indicates whether there has been a monotonic increase or decrease over the last two weeks leading up to a given data point, or an unclear trend. Forecasts that aren’t scored (because there was no complete set of death forecasts available) are greyed out. B, D: Visualisation of corresponding WIS. The shape indicates whether the trend was rising, falling or unclear at the date when the corresponding forecast was made (i.e. two weeks earlier, which leads to a shift of two weeks when compared to panels A and C)"
```

@@

```{r}
caption <- ""
```

@@

```{r}
caption <- "Visualisation of aggregate performance metrics across forecast horizons for the different versions of the Hub ensemble. “Hub-ensemble” excludes all our models, Hub-ensemble-all includes all of our models, “Hub-ensemble-real” is the real hub-ensemble with the renewal model and the crowd forecasts included. Values (except for Bias) are computed as differences to the Hub ensemble excluding our contributions. For Coverage, this is an absolute difference, for other metrics this is a percentage difference. A: mean weighted interval score (WIS) across horizons. B: median WIS. C: Absolute error of the median forecast. D: Standard deviation of the WIS. E: Sharpness (higher values mean greater dispersion of the forecast). F: Bias, i.e. general tendency to over- or underpredict. Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally. G: Empirical coverage of the 50\\% prediction intervals. F: Empirical coverage of the 90\\% prediction intervals"
```

@@

<!-- Our contributions consistently improved the pre-existing Hub ensemble for cases, but not for deaths. We often found contributions to an ensemble to be beneficial even in instances where the forecasting approach entering the ensemble performed consistently worse than the pre-existing ensemble.   -->

@@

In general, our results support the use of ensembles, rather than individual models to inform public health policies, as these provide consistently good performance and largely avoid particularly bad outlier forecasts. Our results also suggest that at least for a small ensemble like the German and Polish Forecast Hub ensemble tends to be beneficial in most instances (with the version of the hub ensemble that includes all our contributions ("hub-ensemble-with-all") outperforming the realised official hub ensemble in almost all instances). We often found contributions to an ensemble to be beneficial even in instances where the forecasting approach entering the ensemble performed consistently worse than the pre-existing ensemble. Including more models may be easier when using a median ensemble, as extreme forecasts tend to have less of an influence there. Individual models, however, can still have a place in informing public policy. As an average, ensembles show the consensus opinion, which implies that in contrast to single models, they are not likely to reveal information, e.g. about future changes in trend, that is not in some way ‘obvious’ to the majority of forecasters.

In the context of evaluating different models and the merits of human intervention, what constitutes a ‘good’ forecast very much depends on the purpose of that forecast. Policymakers may care much more about certain types of errors, (e.g. under-prediction) than others in a way not captured by the weighted interval score. Also, it is helpful to distinguish between ‘forecasts’ and ‘projections’. For example, the outperformance of the crowd forecasts on cases and in general on longer forecast horizons is perhaps not surprising, given that humans could factor in an expectation of future changes in conditions (e.g. future policy interventions, adherence to these interventions, testing policy, and the evolution of new disease variants) while our model-based forecasts could not. However, if the aim of a forecast is to inform policy and decision making, then attempting to factor in the interventions one is meant to inform may be problematic (and conversely, arguing for or against interventions based on predictions may be difficult depending on what the forecast assumes about future interventions). In that sense, crowd forecasts can be understood as forecasts, whereas our model predictions may be better understood as projections that show what would happen in the absence of any events that could change the trend. This may pose a problem in the context of a forecast hub if teams have a different understanding about the purpose of a forecast. Projections that are meant to inform policy makers about possible scenarios may be different from forecasts meant to inform the general public, and yet again different from forecasts submitted with the goal of advancing open research and in order to allow public scrutiny and discussion about the merits of different approaches.

Further work should explore the effects of human intervention on model-based forecasts in more detail. Model-based forecasts could be used as an input to human judgement, with researchers adjusting predictions generated by models. Seeing a model-based forecasts could help humans calibrate uncertainty better, while allowing for manual intervention to adapt spurious trend predictions. Tools need to be developed to facilitate this process at a larger scale. Human insight could also be used as an input to models. Such a ‘hybrid’ forecasting approach could for example ask humans to predict the trend of the effective reproduction number $R_t$ or the doubling rate (i.e. how the epidemic evolves) into the future and use this to estimate the exact number of cases, hospitalisations or deaths this would imply. This approach seems especially promising for forecasting deaths if a model can accurately describe delay distributions and epidemiological relationships between different parameters. In light of severe overconfidence, yet good performance in terms of the absolute error, post-processing of human forecasts to adjust and widen confidence intervals may be another promising approach. Crowd forecasting in general could benefit greatly from the availability of tools suitable to appeal to a greater audience. Given the good performance we and previous authors observed in spite of the limited resources available and the small number of participants, this seems worthwhile for researchers and policymakers to further develop and explore.

@@

# saveRDS(data, file = "tables/scores-table.rds")

library(kableExtra)
library(magrittr)
library(knitr)
data[, 1:2] %>%
  kableExtra::kbl(format = "latex", booktabs = TRUE, 
                  escape = FALSE,
                  caption = "Overview of the scoring metrics used.",
                  longtable = TRUE,
                  linesep = c('\\addlinespace \\addlinespace')) %>%
  kableExtra::column_spec(1, width = "2.5cm") %>%
  kableExtra::column_spec(2, width = "13.0cm") %>%
  # kableExtra::column_spec(3, width = "4.5cm") %>%
  kableExtra::kable_styling(latex_options = c("striped", "repeat_header"))

@@

@@

\begin{align}
  I_{t} &= I_0 \exp  \left(r t \right)  \\
  I_0 &\sim \mathcal{LN}(\log I_{obs}, 0.2) \\
  r &\sim \mathcal{LN}(r_{obs}, 0.2) \\
\end{align}

@@

Where,
\begin{align}
     w &\sim \mathcal{G}(\mu_{w}, \sigma_{w}) \\
    \xi_{O} &\sim \mathcal{LN}(\mu_{\xi_{O}}, \sigma_{\xi_{O}}) \\
    \xi_{D} &\sim \mathcal{LN}(\mu_{\xi_{D}}, \sigma_{\xi_{D}}) \\
\end{align}

@@

\begin{align}
    \mu_{\xi_{D}} &\sim \mathcal{N}(2.29, 0.076) \\
    \sigma_{\xi_{D}} &\sim \mathcal{N}(0.76, 0.055) \\
    \alpha &\sim \mathcal{N}(0.005, 0.0025) \\
\end{align}

@@

@@

```{r}
caption <- ""
```

```{r score-table-2}
```

```{r}
caption <- ""
```

```{r score-table-4}
```

@@

### Performance across locations in absolute terms
```{r}
caption <- ""
```

@@

```{r}
caption <- ""
```

@@

```{r}
caption <- ""
```

@@

### Visualisation of scores and forecasts 1, 3, 4 weeks ahead

```{r}
caption <- ""
```

@@

```{r}
caption <- ""
```

@@

```{r}
caption <- ""
```

@@

### Distribution of scores for 1, 3, 4 week-ahead forecasts

```{r}
caption <- ""
```

@@

```{r}
caption <- ""
```

@@

```{r}
caption <- ""
```

@@

```{r}
caption <- ""
```

@@

@@

- tables for limited period
- plot for limited period

@@

  list(Name = "", Explanation = ""),
  list(
    Name = "Crowd forecast", 
    `Explanation` = "Submitted to the Forecast Hub as 'epiforecasts-EpiExpert'"
  ),  
  list(
    Name = "Renewal model", 
    `Explanation` = "Submitted to the Forecast Hub as 'epiforecasts-EpiNow2'"
  ),  
  list(
    Name = "Convolution model", 
    `Explanation` = "Submitted to the Forecast Hub as 'epiforecasts-EpiNow2\\_secondary'"
  )
) %>%
  kableExtra::kbl(format = "latex", booktabs = TRUE, 
                  escape = FALSE,
                  caption = "Overview of the models and ensembles used.",
                  longtable = TRUE,
                  linesep = c('\\addlinespace \\addlinespace')) %>%
  kableExtra::column_spec(1, width = "4.5cm") %>%
  kableExtra::column_spec(2, width = "11.0cm") %>%
  # kableExtra::column_spec(3, width = "4.5cm") %>%
  kableExtra::kable_styling(latex_options = c("striped", "repeat_header"))

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, 
                      out.width = "100%", 
                      fig.pos = "H", out.extra = "")
library(kableExtra)
library(magrittr)
library(knitr)
```

@@

```{r}
caption <- "Visualisation of aggregate performance metrics across forecast horizons. A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons. WIS is decomposed into its components dispersion, over-prediction and under-prediction. C: Empirical coverage of the 50\\% prediction intervals (50\\% coverage is perfect). D: Empirical coverage of the 90\\% prediction intervals. E: Dispersion (same as in panel A, B). Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score. F: Bias, i.e. general (relative) tendency to over- or underpredict. Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally. G: Absolute error of the median forecast (lower is better). H. Standard deviation of all WIS values for different horizons"
```

```{r agg-performance-all, fig.cap=caption}
knitr::include_graphics("../analysis/plots/aggregate-performance-all-v4.png")
```

```{r}
caption <- "A, C: Visualisation of 50\\% prediction intervals of two week ahead forecasts against the true observed values. Forecasts that were not scored (because there was no complete set of death forecasts available) are greyed out. B, D: Visualisation of corresponding WIS."
```

@@

```{r}
caption <- "A: Distribution of weighted interval scores for two week ahead forecasts of the different models and forecast targets. B: Distribution of WIS separate by country."
```

@@

```{r}
caption <- "Visualisation of aggregate performance metrics across forecast horizons for the different versions of the Hub median ensemble. “Hub-ensemble” excludes all our models, Hub-ensemble-all includes all of our models, “Hub-ensemble-real” is the real hub-ensemble with the renewal model and the crowd forecasts included. Values (except for Bias) are computed as differences to the Hub ensemble excluding our contributions. For Coverage, this is an absolute difference, for other metrics this is a percentage difference. A: mean weighted interval score (WIS) across horizons. B: median WIS. C: Absolute error of the median forecast. D: Standard deviation of the WIS. E: Dispersion (higher values mean greater spread of the forecast). F: Bias, i.e. general tendency to over- or underpredict. Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally. G: Empirical coverage of the 50\\% prediction intervals. F: Empirical coverage of the 90\\% prediction intervals"
```

@@

@@

In general, our results support the use of ensembles, rather than individual models to inform public health policies, as these provide consistently good performance and largely avoid particularly bad outlier forecasts. Our results also suggest that at least for a small median ensemble like the German and Polish Forecast Hub ensemble adding more models may increase performance in most instances (with the version of the hub ensemble that includes all our contributions ("hub-ensemble-with-all") outperforming the realised official hub ensemble in almost all instances). We often found contributions to an ensemble to be beneficial even in instances where the forecasting approach entering the ensemble performed consistently worse than the pre-existing ensemble. Including more models may be easier when using a median ensemble, as extreme forecasts tend to have less of an influence there. Individual models, however, can still have a place in informing public policy. As an average, ensembles show the consensus opinion, which implies that in contrast to single models, they are not likely to reveal information, e.g. about future changes in trend, that is not in some way ‘obvious’ to the majority of forecasters.

In the context of evaluating different models and the merits of human intervention, what constitutes a ‘good’ forecast very much depends on the purpose of that forecast. Policymakers may care much more about certain types of errors, (e.g. under-prediction) than others in a way not captured by the weighted interval score. Also, it is helpful to distinguish between ‘forecasts’ and ‘projections’. For example, the outperformance of the crowd forecasts on cases and in general on longer forecast horizons is perhaps not surprising, given that humans could factor in an expectation of future changes in conditions (e.g. future policy interventions, adherence to these interventions, testing policy, and the evolution of new disease variants) while our model-based forecasts could not. However, if the aim of a forecast is to inform policy and decision making, then attempting to factor in the interventions one is meant to inform may be problematic (and conversely, arguing for or against interventions based on predictions may be difficult depending on what the forecast assumes about future interventions). In that sense, crowd forecasts can be understood as forecasts, whereas our model predictions may be better understood as projections that show what would happen in the absence of any events that could change the trend. This may pose a problem in the context of a forecast hub if teams have a different understanding about the purpose of a forecast. Projections that are meant to inform policy makers about possible scenarios may be different from forecasts meant to inform the general public, and yet again different from forecasts submitted with the goal of advancing open research and in order to allow public scrutiny and discussion about the merits of different approaches.   
Further work should explore the effects of human intervention on model-based forecasts in more detail. Model-based forecasts could be used as an input to human judgement, with researchers adjusting predictions generated by models. Seeing a model-based forecasts could help humans calibrate uncertainty better, while allowing for manual intervention to adapt spurious trend predictions. Tools need to be developed to facilitate this process at a larger scale. Human insight could also be used as an input to models. Such a ‘hybrid’ forecasting approach could for example ask humans to predict the trend of the effective reproduction number $R_t$ or the doubling rate (i.e. how the epidemic evolves) into the future and use this to estimate the exact number of cases, hospitalisations or deaths this would imply. This approach seems especially promising for forecasting deaths if a model can accurately describe delay distributions and epidemiological relationships between different parameters. In light of severe overconfidence, yet good performance in terms of the absolute error, post-processing of human forecasts to adjust and widen confidence intervals may be another promising approach. Crowd forecasting in general could benefit greatly from the availability of tools suitable to appeal to a greater audience. Given the good performance we and previous authors observed in spite of the limited resources available and the small number of participants, this seems worthwhile for researchers and policymakers to further develop and explore.

# (APPENDIX) Supplementary information {-}

@@

data[, 1:2] %>%
  kableExtra::kbl(format = "latex", booktabs = TRUE, 
                  escape = FALSE,
                  caption = "Overview of the scoring metrics used.",
                  longtable = TRUE,
                  linesep = c('\\addlinespace \\addlinespace')) %>%
  kableExtra::column_spec(1, width = "2.5cm") %>%
  kableExtra::column_spec(2, width = "13.0cm") %>%
  kableExtra::kable_styling(latex_options = c("striped", "repeat_header"))

@@

\clearpage

@@

\begin{align}
  I_{t} &= I_0 \exp  \left(r t \right)  \\
  I_0 &\sim \mathcal{LN}(\log I_{obs}, 0.2) \\
  r &\sim \mathcal{LN}(r_{obs}, 0.2) 
\end{align}

@@

Where,
\begin{align}
     w &\sim \mathcal{G}(\mu_{w}, \sigma_{w}) \\
    \xi_{O} &\sim \mathcal{LN}(\mu_{\xi_{O}}, \sigma_{\xi_{O}}) \\
    \xi_{D} &\sim \mathcal{LN}(\mu_{\xi_{D}}, \sigma_{\xi_{D}}) 
\end{align}

@@

\begin{align}
    \mu_{\xi_{D}} &\sim \mathcal{N}(2.29, 0.076) \\
    \sigma_{\xi_{D}} &\sim \mathcal{N}(0.76, 0.055) \\
    \alpha &\sim \mathcal{N}(0.005, 0.0025) 
\end{align}

@@

\clearpage

```{r}
add_caption <- function(table, caption) {
  table <- gsub(pattern = "begin\\{table\\}\\[!h\\]",
                replacement = paste0("begin\\{table\\}[!h]\n\\\\caption\\{",
                                     caption,
                                     "\\\\\\\\\\\\hspace{\\\\textwidth}\\}\n"),
                x = table)
  return(table)
}
```

@@

```{r}
caption <- 
  "Scores for one and two week ahead forecasts (cut to three significant digits and rounded). Note that scores for cases (which include the whole period from October 12th 2020 until March 1st 2021) and deaths (which include only forecasts from the 21st of December 2020 on) are computed on different subsets. Numbers in brackets show the metrics relative to the Hub ensemble (i.e. the median ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions). WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model. Dispersion, over-prediction and under-prediction together sum up to the weighted interval score. Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict. 50\\\\% and 90\\\\%-coverage are the percentage of observed values that fell within the 50\\\\% and 90\\\\% prediction intervals of a model."
```

```{r score-table-2}
table <- readRDS("../analysis/plots/table_scores_2_ahead.rds")
add_caption(table, caption)
```

```{r}
caption <- gsub(x = caption, pattern = "one and two", replacement = "three and four")
```

```{r score-table-4}
table <- readRDS("../analysis/plots/table_scores_4_ahead.rds")
add_caption(table, caption)

\clearpage

@@

### Performance across locations in absolute terms
```{r}
caption <- "Visualisation of aggregate performance metrics across locations. A: mean weighted interval score (WIS) across horizons. B: median WIS. C: Absolute error of the median forecast. D: Standard deviation of the WIS. E: Sharpness (higher values mean greater dispersion of the forecast). F: Bias, i.e. general tendency to over- or underpredict. Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally. G: Empirical coverage of the 50\\% prediction intervals. F: Empirical coverage of the 90\\% prediction intervals."
```

@@

```{r}
caption <- " Visualisation of aggregate performance metrics across locations relative to the Hub ensemble (excluding our contributions). A: mean weighted interval score (WIS) across horizons. B: median WIS. C: Absolute error of the median forecast. D: Standard deviation of the WIS. E: Sharpness (higher values mean greater dispersion of the forecast). F: Bias, i.e. general tendency to over- or underpredict. Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally. G: Empirical coverage of the 50\\% prediction intervals. F: Empirical coverage of the 90\\% prediction intervals."
```

@@

```{r}
caption <- "Visualisation of daily report data. The black line represents weekly data divided by seven. Data were last accessed through the German and Polish Forecast Hub on August 21 2021."
```

@@

\clearpage

## Visualisation of scores and forecasts 1, 3, 4 weeks ahead

```{r}
caption <- "A, C: Visualisation of 50\\% prediction intervals of one week ahead forecasts against the true observed values. Forecasts that were not scored (because there was no complete set of death forecasts available) are greyed out. B, D: Visualisation of corresponding WIS."
```

@@

```{r}
caption <- gsub(x = caption, pattern = "one", replacement = "three")
```

@@

```{r}
caption <- gsub(x = caption, pattern = "three", replacement = "four")
```

@@

\clearpage

## Distribution of scores

### Absolute scores

```{r}
caption <- "A: Distribution of weighted interval scores for one week ahead forecasts of the different models and forecast targets. B: Distribution of WIS separate by country."
```

@@

```{r}
caption <- "A: Distribution of the ranks (determined by the weighted interval score) for one week ahead forecasts of the different models and forecast targets. B: Distribution of ranks separate by country."
```

@@

```{r}
caption <- gsub(x = caption, pattern = "one", replacement = "two")
```

@@

```{r}
caption <- gsub(x = caption, pattern = "two", replacement = "three")
```

@@

\clearpage

## Comparison of ensembles

### Performance visualisation mean ensemble

```{r}
caption <- "Visualisation of aggregate performance metrics across forecast horizons for the different versions of the Hub mean ensemble. “Hub-ensemble” excludes all our models, Hub-ensemble-all includes all of our models, “Hub-ensemble-real” is the real hub-ensemble with the renewal model and the crowd forecasts included. Values (except for Bias) are computed as differences to the Hub ensemble excluding our contributions. For Coverage, this is an absolute difference, for other metrics this is a percentage difference. A: mean weighted interval score (WIS) across horizons. B: median WIS. C: Absolute error of the median forecast. D: Standard deviation of the WIS. E: Dispersion (higher values mean greater spread of the forecast). F: Bias, i.e. general tendency to over- or underpredict. Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally. G: Empirical coverage of the 50\\% prediction intervals. F: Empirical coverage of the 90\\% prediction intervals"
```

```{r agg-performance-ensemble-mean, fig.cap=caption}
knitr::include_graphics("../analysis/plots/aggregate-performance-rel-ensemble-mean-v4.png")
```

### Tables median ensemble

```{r}
caption <- 
  "Scores for one and two week ahead forecasts (cut to three significant digits and rounded) for the different versions of the median ensemble. Note that scores for cases (which include the whole period from October 12th 2020 until March 1st 2021) and deaths (which include only forecasts from the 21st of December 2020 on) are computed on different subsets. Numbers in brackets show the metrics relative to the Hub ensemble (i.e. the median ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions). WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model. Dispersion, over-prediction and under-prediction together sum up to the weighted interval score. Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict. 50\\\\% and 90\\\\%-coverage are the percentage of observed values that fell within the 50\\\\% and 90\\\\% prediction intervals of a model."
```

```{r score-table-ensemble-2}
table <- readRDS("../analysis/plots/table_median-ensemble_scores_2_ahead.rds")
add_caption(table, caption)
```

```{r}
caption <- gsub(x = caption, pattern = "one and two", replacement = "three and four")
```

```{r score-table-ensemble-4}
table <- readRDS("../analysis/plots/table_median-ensemble_scores_4_ahead.rds")
add_caption(table, caption)
```

### Tables mean ensemble

```{r}
caption <- 
  "Scores for one and two week ahead forecasts (cut to three significant digits and rounded) for the different versions of the mean ensemble. Note that scores for cases (which include the whole period from October 12th 2020 until March 1st 2021) and deaths (which include only forecasts from the 21st of December 2020 on) are computed on different subsets. Numbers in brackets show the metrics relative to the Hub mean ensemble (i.e. the mean ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions). WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model. Dispersion, over-prediction and under-prediction together sum up to the weighted interval score. Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict. 50\\\\% and 90\\\\%-coverage are the percentage of observed values that fell within the 50\\\\% and 90\\\\% prediction intervals of a model."
```

```{r score-table-ensemble-mean-2}
table <- readRDS("../analysis/plots/table_mean-ensemble_scores_2_ahead.rds")
add_caption(table, caption)
```

```{r}
caption <- gsub(x = caption, pattern = "one and two", replacement = "three and four")
```

```{r score-table-ensemble-mean-4}
table <- readRDS("../analysis/plots/table_mean-ensemble_scores_4_ahead.rds")
add_caption(table, caption)
```

\clearpage

@@

In the original analysis, cases and deaths were scored on different periods, as the convolution model was only added later. This sensitivity shows performance of all models restricted to the period from October 14 2020 until March 1st 2021 where all models were available.

```{r}
caption <- "Visualisation of aggregate performance metrics across forecast horizons only for the period from October 14th 2020 on where all models were available. A, B: mean weighted interval score (WIS, lower indicates better performance) across horizons. WIS is decomposed into its components dispersion, over-prediction and under-prediction. C: Empirical coverage of the 50\\% prediction intervals (50\\% coverage is perfect). D: Empirical coverage of the 90\\% prediction intervals. E: Dispersion (same as in panel A, B). Higher values mean greater dispersion of the forecast and imply ceteris paribus a worse score. F: Bias, i.e. general (relative) tendency to over- or underpredict. Values are between -1 (complete under-prediction) and 1 (complete over-prediction) and 0 ideally. G: Absolute error of the median forecast (lower is better). H. Standard deviation of all WIS values for different horizons"
```

```{r agg-performance-all-late, fig.cap=caption}
knitr::include_graphics("../analysis/plots/aggregate-performance-all-late-period-v4.png")
```

```{r}
caption <- 
  "Scores for one and two week ahead forecasts (cut to three significant digits and rounded) calculated on forecasts made between December 14th 2020 and March 1st 2021. Numbers in brackets show the metrics relative to the Hub ensemble (i.e. the median ensemble of all other models submitted to the German and Polish Forecast Hub, excluding our contributions). WIS is the mean weighted interval score (lower values are better), WIS - sd is the standard deviation of all scores achieved by a model. Dispersion, over-prediction and under-prediction together sum up to the weighted interval score. Bias (between -1 and 1, 0 is ideal) represents the general average tendency of a model to over- or underpredict. 50\\\\% and 90\\\\%-coverage are the percentage of observed values that fell within the 50\\\\% and 90\\\\% prediction intervals of a model."
```

```{r score-table-late-2}
table <- readRDS("../analysis/plots/table-late-period_2_ahead.rds")
add_caption(table, caption)
```

```{r}
caption <- gsub(x = caption, pattern = "one and two", replacement = "three and four")
```

```{r score-table-late-4}
table <- readRDS("../analysis/plots/table-late-period_4_ahead.rds")
add_caption(table, caption)

\clearpage

## Overview of models and forecasters

@@

  list(Name = "", Explanation = ""),
  list(
    Name = "Crowd forecast", 
    `Explanation` = "Submitted to the Forecast Hub as 'epiforecasts-EpiExpert'"
  ),  
  list(
    Name = "Renewal model", 
    `Explanation` = "Submitted to the Forecast Hub as 'epiforecasts-EpiNow2'"
  ),  
  list(
    Name = "Convolution model", 
    `Explanation` = "Submitted to the Forecast Hub as 'epiforecasts-EpiNow2\\_secondary'"
  )
) %>%
  kableExtra::kbl(format = "latex", booktabs = TRUE, 
                  escape = FALSE,
                  caption = "Overview of the models and ensembles used.",
                  longtable = TRUE,
                  linesep = c('\\addlinespace \\addlinespace')) %>%
  kableExtra::column_spec(1, width = "4.5cm") %>%
  kableExtra::column_spec(2, width = "11.0cm") %>%
  kableExtra::kable_styling(latex_options = c("striped", "repeat_header")) 
```

```{r num-forecasters, fig.cap="Number of participants who submitted a forecast over time."}
knitr::include_graphics("../analysis/plots/number-forecasters.png")
```

```{r num-ensemble-members, fig.cap="Number of member models (including our crowd forecasts and the renewal model) in the official Hub ensemble. Note that the renewal model was not included in the ensemble on December 28th 2020."}
knitr::include_graphics("../analysis/plots/ensemble-members.png")
```

\clearpage
